HTW Test Analysis

### 2023-07-31 Analysis/data_organize.qmd

saveRDS(d,here(paste0("data/dAll_",date.append,".rds")))
saveRDS(e1,here(paste0("data/e1_",date.append,".rds")))
saveRDS(e2,here(paste0("data/e2_",date.append,".rds")))
saveRDS(e3,here(paste0("data/e3_",date.append,".rds")))

>>>>

# saveRDS(d,here(paste0("data/dAll_",date.append,".rds")))
# saveRDS(e1,here(paste0("data/e1_",date.append,".rds")))
# saveRDS(e2,here(paste0("data/e2_",date.append,".rds")))
# saveRDS(e3,here(paste0("data/e3_",date.append,".rds")))

### 2023-07-31 Analysis/test_analysis-all.qmd

```{r}
pacman::p_load(tidyverse,data.table,lme4,emmeans,here)
d <- readRDS(here("data/dPrune-05-21-23.rds"))

@@

dtestAgg <- dtest %>% group_by(id,condit,catOrder,fb,vb,band,lowBound,highBound,input) %>% mutate(vxCapped=ifelse(vx>1600,1600,vx)) %>%
  summarise(vxMean=mean(vx),devMean=mean(dist),vxMed=median(vx),devMed=median(dist),
            vxMeanCap=mean(vxCapped),.groups = "keep")

```{r}
model <- lmer(devMean ~ condit * catOrder * fb + (1|id), data = dtestAgg)
summary(model)

```
Linear mixed model fit by REML ['lmerMod']
Formula: devMean ~ condit * catOrder * fb + (1 | id)
   Data: dtestAgg

>>>>

```{r}
pacman::p_load(tidyverse,data.table,lme4,emmeans,here,knitr,kableExtra)
d <- readRDS(here("data/dPrune-05-21-23.rds"))

@@

dtestAgg <- dtest %>% group_by(id,condit,catOrder,fb,vb,band,lowBound,highBound,input) %>% mutate(vxCapped=ifelse(vx>1600,1600,vx)) %>%
  summarise(vxMean=mean(vx),devMean=mean(dist),vxMed=median(vx),devMed=median(dist),
            vxMeanCap=mean(vxCapped),.groups = "keep")
```

```{r}
model <- lmer(devMean ~ condit * catOrder * fb + (1|id), data = dtestAgg)
summary(model)
```

Linear mixed model fit by REML ['lmerMod']
Formula: devMean ~ condit * catOrder * fb + (1 | id)
   Data: dtestAgg
